Energy and the CES production function

### 2015-09-17 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
new plots

@@

>>>>

<<>>=
leaf_apply(models, function(mod, id) class(mod), class="cesModel")
@

<<output-elasticity>>=
mod2oedf <- function(mod, id){
  # Parse the id to find out whether this is quality-adjusted data, etc.
  ### Don't name non-lists with variables whose names sound like a list.
  ### I'm guessing you just didn't know what kind of data you were working with here. 
  ### Either way, it's a bad thing.
  id_components <- strsplit(id, split = "[.]")[[1]]

  ### NOTE: data_frame does not auto-convert to factors.  It leaves things as strings.
  message(class(mod))
  if (! inherits(mod, "cesModel") ) return(NULL)

  fortify(mod) %>%
    mutate(
      Country = id_components[1], 
      flavor  = ifelse(id_components[2]=="unadjusted", "Unadjusted", "Quality-adjusted"),
      energy  = ifelse(id_components[3]=="noE", "Without energy", "With energy"),
      model   = id_components[4], 
      nest    = id_components[5]
    ) 
}

AllOE <- 
  leaf_apply(
    models, 
    class = "cesModel", 
    mod2oedf
  ) %>% 
  bind_rows()
@

@@

<<>>=
OEplot <- function( data ) {
  ggplot( data %>% 
          mutate(
            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
            )
          ) +
    tri_theme() +
    tri_grid() +
    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
    geom_tripath( 
      aes(x=oe1, y=oe2, z=oe3, 
          colour = Year,
          group=interaction(Country, nest, flavor)),
      alpha=0.6,  size=1) +
    geom_tripoint( 
      aes(x=oe1, y=oe2, z=oe3, colour = Year, size=Year), 
      alpha=0.7, shape=21)  +
    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
    facet_grid(nest ~ slice) +
    scale_size_continuous( range = c(1.4, 4))
}
OEplot(AllOE) 
@

<<>>=
require(tidyr)
ggplot(AllOE %>% 
         mutate(split = as.character(
           interaction(Country, flavor, lex.order = TRUE))) %>%
         gather(factor, elasticity, oe1, oe2, oe3), aes(x=Year)) +
  geom_line( 
    alpha = .5, size=1.8,
    aes(y = elasticity, 
        colour = factor, 
        linetype=flavor
    ) ) +
  facet_grid(nest ~ Country) +
  theme_minimal() 
@

<<>>=
ggplot(AllOE %>% mutate(split = interaction(Country, flavor, lex.order=TRUE))) +
  tri_theme() + 
  tri_grid() +
  tri_labels( labels = c("alpha[k]", "alpha[l]", "alpha[e]") ) +
  geom_tripath(alpha = 0.8, size = 1.2,
               aes(x = oe1, y = oe2, z = oe3,
                   colour = Year, group = interaction(Country, nest, flavor)
               ) ) +
#  geom_tripoint( size = 1.8, alpha = 0.5,
#                 aes(x = oe1, y = oe2, z = oe3,
#                     shape = flavor,
#                     colour = Year
#                 ) ) +
  facet_grid( nest~ split) + 
  scale_shape_manual(values = c(21:25)) +
  scale_colour_gradient2(low = scales::muted("navy"), mid="red", high = "green", midpoint = 1985)
